---
title: "Econometrics Pset 1"
author: "Bridger Gordon"
date: "2/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Clear the workspace 
rm(list=ls())

# Install and load packages
library(haven)
library(tidyverse)
library(sandwich)
library(lmtest)

# Load in the stata dataset
health <- read_dta("healthinequality.dta")

```

## Question 1

```{r model}

model1 <- lm(life_exp ~ cur_smoke, data = health) 

#heteroskedacity-only
summary(model1)

#heteroskedacity-robust
coeftest(model1, vcov = vcovHC(model1, type="HC1"))

```

Equation Form: y = 78.4936 + (-7.4460) * cur_smoke

a) the coefficient (-7.4460) represents that an increase of 10 percentage points to smoking is associated with a 0.7446 year decrease to life expectancy.

b) r squared is 0.1208 -- tells us that there are other factors that also explain it (this explains 12% of the variability)

c) ??

d) robust has larger standard error and is more reliable

## Question 2

1.96 * 1.11506 = margin of error = 2.1855176

(-9.6315, -5.2604)

## Question 3
What range of estimates do the lower and upper bounds on the confidence interval allow you to rule out?

Allows us to rule out / reject slope coefficient less than 9.63 or greater than -5.26

## Question 4

```{r multimodel}

model2 <- lm(life_exp ~ cur_smoke + bmi_obese + exercise, data = health) 

#heteroskedacity-only
summary(model2)

#heteroskedacity-robust
coeftest(model2, vcov = vcovHC(model2, type="HC1"))

```

a) an increase of 10 pp to the share of people exercising is associated with an increase of 0.56 years in life expectancy on average

b) yes, smoking and obesity reduce life expectancy and exercise increases it

## Question 5

tables

## Question 6

a) 

b) wealth / class ?



```{r}
#Run regression with homoskedasticity-only standard errors 
#mod1 <- lm(yvar~xvar1+xvar2 + xvar3, data = health) 
#summary(mod1)
#Report coefficients with heteroskedasticity robust standard errors 
#coeftest(mod1, vcov = vcovHC(mod1, type="HC1"))

#Store residuals from regression of yvar on xvar1 and xvar3 
#m1 <- lm(yvar ~ xvar1+ xvar3, data = health)
#y.uhat.resid <- m1$residuals

# Draw scatter plot with linear fit line
#ggplot() + geom_point(aes(x = xvar1, y = yvar)) +
#geom_smooth(aes(x = xvar, y = yvar), method = "lm", se = F)
#Save graph as figure1a.png ggsave("figure1a.png")

#sink(file="ps1_log.txt", split=TRUE) 
#sink()
```

